% !TEX root = Paper.tex

In this section, the simulation results of the proposed control strategy are presented. The simulations are performed using MATLAB/Simulink, and the system parameters are listed in Table \ref{tab:params}. The proposed control strategy is tested under grid unbalanced swell, load impact, load unbalance, and non-linear load conditions.

\begin{table}[h!]
    \centering
    \caption{System Parameters}
    \begin{tabular}{|c|c|c|}
        \hline
        Parameter & Variable & Value \\
        \hline
        \hline
        Grid Voltage & $V_{g}$ & 10 kV \\
        Nominal Converter Voltage & $V_s$ & 400 V \\
        DC Link Voltage & $V_{DC}$ & 700 V \\
        Grid Frequency & $f_e$ & 50 Hz \\
        Series Converter Filter Inductance & $L_{fs}$ & $200\ \mu\text{H}$ \\
        Series Converter Filter Resistance & $R_{fs}$ & $100\ \text{m}\Omega$ \\
        Series Converter Filter Capacitance & $C_{fs}$ & $12\ \mu\text{F}$ \\
        Parallel Converter Filter Inductance & $L_{fp}$ & $200\ \mu\text{H}$ \\
        Parallel Converter Filter Resistance & $R_{fp}$ & $100\ \text{m}\Omega$ \\
        Parallel Converter Filter Capacitance & $C_{fp}$ & $12\ \mu\text{F}$ \\
        Transformer Dispersion Inductance & $L_Y$ & $100\ \mu\text{H}$ \\
        Transformer Series Resistance & $R_Y$ & $5\ \text{m}\Omega$\\
        Coupling Transformer Turns Ratio & $N_{CT}$ & $5$ \\
        Distribution Transformer Turns Ratio & $N_{DT}$ & $V_s/(V_g\sqrt{3})$ \\
        Converters Switching Frequency & $f_{\text{sw}}$ & 20 kHz \\
        Control Sampling Time & $T_s$ & 50 µs \\
        \hline
    \end{tabular}
    \label{tab:params}
\end{table}

Each of the load impacts are comprised by $47\ \Omega$ resistive load per phase, $2\ k\Omega$ resistive load in phase $a$ for the unbalanced load, and a three-phase diode bridge rectifier with a $47\ \Omega$ resistive load at its output for the non-linear load. The simulation results are shown in \Cref{fig:Sim_results}.

\subsection{Grid Voltage Unbalanced Swell Compensation}

From the instant $t = 10\ ms$ until $t = 260\ ms$, a three-phase unbalanced swell of $10\%$ the nominal value, in phase $b$ is applied to the grid voltage, as shown in \Cref{fig:Sim_results}.(a). The proposed control strategy effectively compensates for the unbalanced swell, meaning that the parallel inverter injects the necessary voltage to maintain a balanced transformer secondary side current, as shown in \Cref{fig:Sim_results}.(d).

\subsection{Load Impact}

At $t = 60\ ms$, a three-phase balanced load impact of $47\ \Omega$ per phase is applied, as shown in \Cref{fig:Sim_results}.(b). In this case, the parallel converter injects the necessary current to maintain the transformer secondary side current, in particular after the load impact, as shown in \Cref{fig:Sim_results}.(e).

\subsection{Unbalanced Load Compensation}

Following the load impacts, at $t = 100\ ms$ an unbalanced load is applied, where phase $a$ has a load of $2\ k\Omega$ and phases $b$ and $c$ have a load of $47\ \Omega$, as shown in \Cref{fig:Sim_results}.(f). The parallel converter injects the necessary current to maintain a balanced transformer secondary side current, as shown in \Cref{fig:Sim_results}.(e).

\subsection{Non-linear Load Compensation}

At $t = 140\ ms$, a three-phase diode bridge rectifier with a $47\ \Omega$ resistive load at its output is applied, as shown in \Cref{fig:Sim_results}.(f). In this case, the parallel converter reference is mainly composed by the fundamental component of the load current, which is extracted using a notch filter. The proposed control strategy manages to compensate this disturbance, maintaining the transformer secondary side current sinusoidal and balanced, as shown in \Cref{fig:Sim_results}.(d).

\subsection{Third Harmonic Compensation}
Finally, at $t = 200\ ms$, a third harmonic component is added to the grid voltage, as shown in \Cref{fig:Sim_results}.(a). In this case, the series converter reference is mainly composed by the fundamental and third harmonic components of the grid voltage, which are extracted using a notch filter. The proposed control strategy effectively compensates for this disturbance, maintaining the transformer secondary side current sinusoidal and balanced, as shown in \Cref{fig:Sim_results}.(d).